### 2016-05-20 intro.tex
cheers

\section{Introduction}
\paragraph{Basic issues in Naor-Yogev. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won't scale in common network applications
\item The main results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters!
\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.  This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.  (If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.)
\item Not sure what Bloom filter-like data structures would have randomized querying procedures (``unsteady representations'').  They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.  But what's the purpose of this, if the security definition gives the adversary the set~$S$?  (What are you keeping private?) 
\end{itemize}

@@

\jknote{Yes, although another way to interpret this is that the adversary cannot find a false positive EVEN IF it had the whitelisted email addresses, even if in practice it does not.}
\tsnote{Fair enough. And this potentially unrealistic attack is preventable by a simple countermeasure.  That said, I'm not convinced the countermeasure is easy to deploy at scale, or that it meshes well with real deployments.  (See below.)  }

@@

\tsnote{UPDATE (5/20/16): I'm now convinced that what they call memory size~$m$, when applied to real Bloom filters, is \emph{only} the size of the bit array, and does \emph{not} include a description of the hash functions.  The memory size comparisons that are made throughout the paper are to classical memory lowerbounds that account only for the bitsize of the array. Concretely: in the abstract they say ``... we show thre exists a Bloom filter for sets of size~$n$ and error~$\epsilon$ , that is secure against~$t$ queries and uses only $O(n\log\frac{1}{\varepsilon} + t)$ bits of memory.  In comparison, $n \log\frac{1}{\varepsilon}$ is the best possible under a non-adaptive adversary.''  The latter bound is the classical one.   If you look in the paper for this actual result, it's in Theorem 6.2.   So, we look at the theorem and the construction that proves it.  It uses a specially constructed function~$g$ and a Cuckoo hashing dictionary~$D$, consisting of two tables~$T_1,T_2$ and two hash functions~$h_1,h_2$.  Here is a quote from the proof ``The final memory of the Bloom filter is the memory of~$D$ and the representation of~$g$.  The dictionary~$D$ consists of $O(n)$ cells, each of size $|g(x)|=O(\log\frac{1}{\varepsilon})$ bits and therefore~$D$ and~$g$ together can be represented using $O(n\log\frac{1}{\varepsilon} + t)$ bits'', where earlier they say ``the representation of~$g$ requires $O(t)$ bits''.  Thus they are \emph{not} considering the size of the hash functions~$h_1,h_2$ that are used to populate the cells of~$D$.   So, as I said, I'm now convinced that their Bloom filter syntax does not actually capture real Bloom filters.}

>>>>

\section{Introduction}
\paragraph{Basic issues in Naor-Yogev. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won't scale in common network applications
\item The main results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters! \tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.}
\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.  This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.  (If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.)
\item Not sure what Bloom filter-like data structures would have randomized querying procedures (``unsteady representations'').  They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.  But what's the purpose of this, if the security definition gives the adversary the set~$S$?  (What are you keeping private?) 
\end{itemize}

@@

\jknote{Yes, although another way to interpret this is that the adversary cannot find a false positive EVEN IF it had the whitelisted email addresses, even if in practice it does not.}
\tsnote{Fair enough. And this potentially unrealistic attack is preventable by a simple countermeasure.  That said, I'm not convinced the countermeasure is easy to deploy at scale, or that it meshes well with real deployments.  (See below.)  } \tsnote{Also, while the adversary is given~$S$ (the whitelisted email addresses), the hash functions used to create the Bloom filter are \emph{secret}.  I'm not convinced this is realistic.}

@@

\tsnote{UPDATE (5/20/16): I'm now convinced that what they call memory size~$m$, when applied to real Bloom filters, is \emph{only} the size of the bit array, and does \emph{not} include a description of the hash functions.  The memory size comparisons that are made throughout the paper are to classical memory lowerbounds that account only for the bitsize of the array. Concretely: in the abstract they say ``... we show there exists a Bloom filter for sets of size~$n$ and error~$\epsilon$, that is secure against~$t$ queries and uses only $O(n\log\frac{1}{\varepsilon} + t)$ bits of memory.  In comparison, $n \log\frac{1}{\varepsilon}$ is the best possible under a non-adaptive adversary.''  The latter bound is the classical one.   If you look in the paper for this actual result, it's in Theorem 6.2.   So, we look at the theorem and the construction that proves it.  It uses a specially constructed function~$g$ and a Cuckoo hashing dictionary~$D$, consisting of two tables~$T_1,T_2$ and two hash functions~$h_1,h_2$.  Here is a quote from the proof ``The final memory of the Bloom filter is the memory of~$D$ and the representation of~$g$.  The dictionary~$D$ consists of $O(n)$ cells, each of size $|g(x)|=O(\log\frac{1}{\varepsilon})$ bits and therefore~$D$ and~$g$ together can be represented using $O(n\log\frac{1}{\varepsilon} + t)$ bits'', where earlier they say ``the representation of~$g$ requires $O(t)$ bits''.  Thus they are \emph{not} considering the size of the hash functions~$h_1,h_2$ that are used to populate the cells of~$D$.   So, as I said, I'm now convinced that their Bloom filter syntax does not actually capture real Bloom filters.}
